### 2017-05-31 paper.tex

The software community's model of collaborative code development is an alternative.
The authors first encountered it in the context of
lessons on basic lab skills for research computing
in the sciences and humanities...

@@

Every day, university instructors and others are writing, teaching, sharing
lessons on subjects as diverse as history, biology, mathematics, or 
technical instruction. Our work overlaps, meaning thousands of hours of 
unnecessary duplication. In these ten simple rules, we provide an alternative: 
adopting the model of collaborative software development to make more robust
and sustainable lessons that can be continually improved. We hope
that the lessons we provide here can help others learn from our experiences
to help us all teach better.

>>>>

The software community's model of collaborative code development is an alternative.
The authors first encountered it in the context of
lessons on basic lab skills for research computing
in the sciences and humanities. They primarily draw on 
their experiences with pedagogical organizations such as 
Software Carpentry and Programming Historian. 
Software Carpentry was founded in 1998 with the goal of 
``making scientists more productive, and their work more
reliable, by teaching them basic computing skills.'' 
They do so through short one or two day intensive workshops that
cover the basics of scientific computing. Programming Historian 
was founded in 2008, and has evolved to become a collaboratively edited
site providing lessons to humanists.

In this article, we strive for an open-source software model, 
by which we mean lesson materials that are:

\item
  Open and easily accessible

\item
  Continually maintained, refined, and 
  improved by a community of contributors

To our knowledge, Software Carpentry (and its related
organizations such as Data Carpentry) are the only real-world
example of an organization satisfying these criteria. Programming
Historian, and other open educational resources, satisfy the
first criteria but not necessarily the latter. While they 
might experience a kind of iterative development where the 
lessons are periodically updated by a small author group
(e.g. this happens when a new edition of an academic 
textbook is released), but this is not the same as regular, 
small releases from a large community of contributors.

Meeting both criteria is critical for two reasons. We need
lessons that are up-to-date with the latest information,
which is crucial given the speed of software development. A lag
between editions means broken dependencies and bugs. Second, lessons
need to continue to live after a key author moves on from 
being able to maintain the lesson.

This all means that the lessons have the potential to be far more useful.
The collective knowledge and experience of the community
is far greater than a single author. The ten simple rules 
that follow aim to help others benefit from the
lessons we have learned as maintainers, editors, and reviewers of 
these resources.

@@

\fixme{65}{Write conclusion}
